Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-01-27 main-disk-model.tex
minor changes from programming

    If the edge is on the disk, it first needs to be read into the memory of the target processor.
    We delay the reads to avoid holding unnecessary files in the memory.
    When we preliminarily schedule a read, we first assess its length and other actions that happen on this processor in the meantime.
    So, the first estimated start of the read is the estimated start time of the task minus the estimated length of the read.
    We then see if this start of the read is happening during the runtime of the previous task or already after it (during the writes).
    If the starting time of the read is during the execution of the previous task and there is enough memory to read this file, then we move the read
    forward to the beginning of this previous task.
    If there is not enough memory, then the entire read is rescheduled for after the task finishes.
    The read will then be bottleneck and affect the eraliest start time of the desired task.

@@

    \subsubsection{On Task Start}
    When a task start event is triggered, it first determines if it can start.
    If some predecessor tasks have not yet finished (the predecessor set is not empty), then the actual time of this event
    is set to the maximum of the estimated end times of predecessor events and this event is reinserted in the queue
    with this new time.

>>>>

    If the edge is on the disk, it first needs to be read into the memory of the target processor.
    We delay the reads to avoid holding unnecessary files in the memory.
    When we preliminarily schedule a read, we first assess its length and other actions that happen on this processor in the meantime.
    So, first estimated start of the read is \skug{the maximum between the desired start time (estimated start time of the task minus the estimated length of the read),
    and the feasible one (when the lastest read event on this processor finishes)}.

    We then see if this start of the read is happening during the runtime of the previous task or already after it (during the writes).
    If the starting time of the read is during the execution of the previous task and there is enough memory to read this file, then we move the read
    forward to the beginning of this previous task.
    If there is not enough memory, then the entire read is rescheduled for after the task finishes.
    The read will then be bottleneck and affect the eraliest start time of the desired task.

@@

    \subsubsection{On Task Start}
    When a task start event is triggered, it first determines if it can start.
    If some predecessor tasks have not yet finished (the predecessor set is not empty), then the actual time of this event
    is set to the maximum of the estimated end times of predecessor events and this event is reinserted in the queue
    with this new time.
    \skug{We  also update the actual times of all its successor events.}
